Turbulence in compact to giant HII regions

### 2021-12-09 strucfunc_paper.tex
Finish description of datasets and make a start on sample sources

%% Package set-up

@@

An alternative way to study turbulent motions is to measure
the fluctuations on the plane of the sky of the velocity centroids of an emission line
\citep{von1951methode}.
We will denote the RMS magnitude of these fluctuations by \(\sigma\pos\).
In addition to being unaffected by the various nuisance broadening mechanisms
discussed in the previous paragraph,
this also offers the opportunity to study the spatial scale of the fluctuations
by measuring average velocity differences as a function of
the angular separation between two points.
Different mathematical tools can be used to study these spatial fluctuations,
such as the autocorrelation function \citep{lagrois2011}
and \(\Delta\)-variance \citep{Ossenkopf:2006a}.
In this work, we will concentrate on the second order structure function,
\(B(r)\) (see section \ref{sec:second-order-struct}),
which has been used in many previous studies of velocity fluctuations
in \hii{} regions in our own Galaxy
% Javier cited the wrong Roy & Joncas here - now corrected (should be 1985 not 1986)
% Also, Medina+ 2014  better than Arthur+ 2016
\citep{munch1958internal, castaneda1988, Roy:1985a, 1992ApJ...387..229O, medina2014}
and in external galaxies
\citep{1961MNRAS.122....1F, tanco1997, lagrois2009multi, lagrois2011, Melnick:2021x}.

@@

@@

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).

@@

Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s. 
The table 1 on their work summarize the propertie of each field.
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

@@

The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
The cumulative integration time per frame is 36 s with a seeing value of 1''.
The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}. The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

\subsection{Regions in the Milky Way and Magellanic Clouds}
\label{sec:regions-milky-way}

@@

@@

@@

@@

@@

@@

@@

\begin{table*}
\begin{center}\caption{Summary of properties.}
\begin{tabular}{ccccc}\hline
HII       &  Distance ($D$)          & Diameter ($R$) & log L(H$_{\alpha}$) &  \(\langle \sigma_{\text{LOS}} \rangle \) \\
Region    &  [kpc]          &  [pc]    &  [erg/s]            &    [km/s]  \\ 
\hline
Orion    & 0.436$\pm$0.02  & 0.6$\pm$0.06  &    37               &   6.0      \\
%Orion large   & 0.436$\pm$0.02  & 5$\pm$0.5    &    37               &   6.0      \\ 
Lagoon    & 1.25$\pm$0.12   & 25$\pm$2.5       &    37.47            &   13.6     \\
Carina    & 2.35$\pm$0.05   & 15$\pm$1.5       &    39.6             &   22.4     \\
30 Dor    & 49.97$\pm$0.19  & 98.9$\pm$9.8     &    39.76            &   31.7     \\
NGC 346   & 61.9$\pm$1.1    & 64$\pm$6.4       &    38.67            &   10.2     \\
Hubble X  & 490$\pm$40      & 160$\pm$16      &    38.6             &   13.4     \\
Hubble V  & 490$\pm$40      & 130$\pm$13 &    38.87            &   12.3     \\
NGC 604   & 820$\pm$30      & 400$\pm$40      &    39.65            &   16.2     \\
NGC 595   & 820$\pm$30      & 400$\pm$40      &    39.36            &   18.3     \\
\hline
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

@@

There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{tanco1997,2019arXiv191203543M}. 
from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
Despite this general agreement the interpretations in each study is different.
\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
None of the previous studies present a power-law index for the structure function to compare our results.
\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.

@@

JGV acknowledges and thanks CONACYT for the PhD research scholarship. We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.

>>>>

%% Package set-up
\usepackage{booktabs}
\usepackage{array}   % for \newcolumntype macro
\newcolumntype{L}{>{$}l<{$}} % math-mode version of lrc column types
\newcolumntype{R}{>{$}r<{$}} 
\newcolumntype{C}{>{$}c<{$}}

@@

An alternative way to study turbulent motions is to measure
the fluctuations on the plane of the sky of the velocity centroids of an emission line
\citep{von1951methode}.
We will denote the RMS magnitude of these fluctuations by \(\sigma\pos\).
In addition to being unaffected by the various nuisance broadening mechanisms
discussed in the previous paragraph,
this also offers the opportunity to study the spatial scale of the fluctuations
by measuring average velocity differences as a function of
the angular separation between two points.
Different mathematical tools can be used to study these spatial fluctuations,
such as the autocorrelation function \citep{lagrois2011}
and \(\Delta\)-variance \citep{Ossenkopf:2006a}.
In this work, we will concentrate on the second order structure function,
\(B(r)\) (see section \ref{sec:second-order-struct}),
which has been used in many previous studies of velocity fluctuations
in \hii{} regions in our own Galaxy
% Javier cited the wrong Roy & Joncas here - now corrected (should be 1985 not 1986)
% Also, Medina+ 2014  better than Arthur+ 2016
\citep{munch1958internal, castaneda1988, Roy:1985a, 1992ApJ...387..229O, medina2014}
and in external galaxies
\citep{1961MNRAS.122....1F, Medina-Tanco:1997a, lagrois2009multi, lagrois2011, Melnick:2021x}.

@@

Wherever possible, we calculate the centroid velocity directly as the first moment
of the line intensity profile for each position on the nebula.
So long as the signal-to-noise is high enough,
this mean velocity can be calculated to a much higher precision
than the nominal velocity resolution of the spectrograph. 
In a few cases, as noted below, we are working with already reduced data,
which are provided in the form of Gaussian fits to the line profiles.
In the cases where multiple Gaussian components have been fitted,
we take the flux-weighted mean velocity of these components to be the centroid.

@@

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are used
to study the Carina Nebula and Lagoon Nebula, respectively.
These were obtained as a by-product of a study of young stars in their respective regions
as part of the Gaia-ESO Spectroscopic Survey \citep{Gilmore:2012v, Randich:2013m}
using VLT/FLAMES with the GIRAFFE and UVES spectrographs \citep{2002Msngr.110....1P}.
The spectra are from multiple discrete fiber positions in each nebula
(866 positions in Carina; 1089 in the Lagoon),
visible as colored disks in Figure~\ref{fig:velocity-maps}.
The angular separation between fibers varies across the maps with
average nearest-neighbor distance of \SI{21 \pm 17}{arcsec}.
The spectral resolution ranges from  \SI{6}{km.s^{-1}} (UVES) to \SI{16}{km.s^{-1}} (GIRAFFE).
We do not have access to the individual spectra, but instead use the
Gaussian fits to the line profiles from \citep{Damiani:2016a, Damiani:2017b},
obtained from data tables downloaded from the CDS Vizier service.\footnote{%
  \url{https://doi.org//10.26093/cds/vizier.35910074} and
  \url{https://doi.org//10.26093/cds/vizier.36040135}.}
For the Lagoon, we use single-Gaussian fits, while for Carina we take the
flux-weighted mean of the blue and red component of two-Gaussian fits.

@@

For the Magellanic Cloud regions 30~Doradus and NGC~346 we use data obtained
with the MUSE spectrograph \citep{Bacon:2010a, Bacon:2014a} on the VLT.\@
Each exposure consists of a \(300 \times 300\) pixel spectral image with a plate scale
of \SI{0.2}{arcsec.pixel^{-1}} and a spectral resolution of \SI{110}{km.s^{-1}}
at \ha{}.
For 30~Doradus, four separate exposures are mosaicked to give a square field of
size \(\SI{2}{arcmin}\) \citep{Castro:2018a}. 
We use centroid velocities of single Gaussian fits to the \ha{} line.\footnote{%
  Data kindly provided by Norberto Castro Rodríguez, priv.~comm.
}
For NGC~346, we use a single field that was observed in 2016 as part of
ESO observing program 098.D-0211(A) (P.I. W.-R.~Hamann).
We obtained the pipeline-reduced data cubes from the ESO data archive\footnote{%
  \url{http://archive.eso.org/wdb/wdb/eso/eso_archive_main/query?prog_id=098.D-0211(A)}
}
and extracted the \ha{} profile using tools in the MPDAF python library.\footnote{
  \url{https://mpdaf.readthedocs.io/en/latest/}
}

@@

The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
\citep{Gordon:2000v}
on the \SI{4.2}{m} William Herschel Telescope (WHT) of
el Roque de los Muchachos Observatory (ORM) in La Palma, Spain
and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
Each velocity image is \(256 \times 256\) pixels on the sky,
with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}}
and a spectral resolution of \SI{40}{km.s^{-1}}.
The NGC~604 observations were previously reported and analysed in
\citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.

% \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
% The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
% The cumulative integration time per frame is 36 s with a seeing value of 1''.
% The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
% Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}. The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

\subsection{Physical properties of the sample regions}
\label{sec:regions-milky-way}

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample}
\begin{tabular}{l CCCC}\toprule
\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion    & 0.436 \pm 0.02  & 0.6 \pm 0.06  &    37               &   6.0      \\
%Orion large   & 0.436 \pm 0.02  & 5 \pm 0.5    &    37               &   6.0      \\ 
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5       &    37.47            &   13.6     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5       &    39.6             &   22.4     \\
30 Dor    & 50.0 \pm 0.2  & 98.9 \pm 9.8     &    39.76            &   31.7     \\
NGC 346   & 62 \pm 1    & 64 \pm 6.4       &    38.67            &   10.2     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.6             &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13 &    38.87            &   12.3     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.65            &   16.2     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    39.36            &   18.3     \\
\bottomrule
\end{tabular}\label{tab:Reg}
\end{center}
\end{table}

\subsubsection{Orion Nebula}
\label{sec:orion-nebula}

@@

\subsubsection{Carina Nebula}
\label{sec:carina-nebula}

@@

\subsubsection{Lagoon Nebula}
\label{sec:lagoon-nebula}

@@

\subsubsection{30 Doradus}
\label{sec:30-doradus}

@@

\subsubsection{NGC 346}
\label{sec:ngc-346}

@@

\subsubsection{Hubble X and Hubble V in NGC 6822}
\label{sec:hubble-x-hubble}

@@

\subsubsection{NGC~595 and NGC~604 in M33}
\label{sec:ngc-595-ngc}

@@

@@

There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{Medina-Tanco:1997a, Melnick:2021x}. 
from \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}, and using the same TAURUS-II data.
Despite this general agreement the interpretations in each study is different.
\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
Interesting enough, \citet{Medina-Tanco:1997a} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
None of the previous studies present a power-law index for the structure function to compare our results.
\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowldgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowldgment}.
Based on observations made with the WHT
\textit{complete WHT acknowldgment}.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
